Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-03 Latex/tex/pr.tex
latex update 2

represents the large scale fading matrix.

@@

It is assumed that we have two processing layer in BBU of O-RAN system. as we mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer. Each VM in both layers map to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VMs in first layer and $M_{s_2}$ VMs in second layer. Each VM in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively. 

>>>>

represents the large scale fading matrix. Here, it is assumed we have perfect channel state information(CSI).

@@

Suppose that we have two processing layer in BBU of O-RAN system. As it is mentioned before, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer. Each VM in both layers map to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VMs in first layer and $M_{s_2}$ VMs in second layer. Each VM in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively. \\
Let the packet arrival of UEs have a Poisson Process with arrival rate $\lambda_{u(v,i)}$ for $i^{th}$ UE in $v^{th}$ service. 
Therefore, the mean arrival data rate of UEs in $s^{th}$ slice is 
$\alpha_s = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  
It is assumed that there are dispatchers in each layer for each slice to divide the incoming traffic to VMs.
Suppose the baseband processing of each VM is depicted as a M/M/1 processing queue.
